\documentclass[letterpaper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{lipsum}

\pagestyle{fancy}
\fancyhf{} 
\renewcommand{\headrulewidth}{0pt}

\lhead{\textbf{Shaik Basheer Ahmed}}
\chead{}
\rhead{\thepage}
\cfoot{}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{multicols}{2}

\section*{Contact Information}
\textbf{Mobile:} 8340976856 \\
\textbf{Email:} basheerahmed23-25@theasb.in \\
\textbf{LinkedIn:}
\url{https://www.linkedin.com/in/basheerahmedshaik/}\\
\textbf{Address:}
Jonnalagadda Mastan Street, Adda Road, Kalara Hospital, Chittinagar, One Town, NTR District, Vijayawada, Andhra Pradesh-520001.

\section*{Objective}
Passionate about Data Science, I bring a deep love for technology and a keen eagerness to explore and master new advancements, fostering innovation and continuous learning.
\section*{Academic}
\textbf{PGDM (Artificial Intelligence and Data Science)} \\
Ashoka School of Business, Aug 2023 - 2025 (Expected Graduation)

\textbf{BSc in IoT} \\
Kakaraparthi Bhavanarayana College, Jul 2019 - Jun 2022 \\
Grade: 6.05

\section{Internship}

\begin{itemize}
    \item Internet of Things (IoT) (Pantech eLearning Solutions Pvt Ltd, Oct 2021)
        \begin{itemize}
            \item Successfully completed a 30-day online internship program.
            \item Gained hands-on experience in:
                \begin{itemize}
                    \item Arduino programming and sensor interfacing
                    \item Data monitoring and real-time applications
                    \item Cloud integration (Azure)
                \end{itemize}
        \end{itemize}
\end{itemize}



\section*{Certification}

\begin{itemize}
    \item \textbf{Ethical Hacking} (Internshala Trainings, Jan 2023)
        \begin{itemize}
            \item Successfully completed an 8-week online training program.
            \item Covered topics include Basics of Information Security, Computer Networking, Web Development, Web Application Vulnerability Assessment and Penetration Testing (VA PT), OWASP Top 10 vulnerabilities, SQL Injections, Client-Side Attacks, and more.
            \item Certificate Number: 811d2gqinbg
        \end{itemize}
\end{itemize}

\begin{itemize}
    \item\textbf{Cyber Security}(ACMEGRADE, IIT Bombay, Aug 2022)
        \begin{itemize}
            \item Successfully completed a program in Cyber Security with a focus on OWASP Top 10. Gained knowledge and skills in identifying and mitigating vulnerabilities based on OWASP Top 10. 
            \item Certificate Number: AGC22070940
        \end{itemize}
\end{itemize}

\section*{Technical Expertise}

\begin{itemize}
  \item Web Development:
    \begin{itemize}
      \item Front-End: Intermediate in HTML, AngularJS, and JavaScript (Building interactive web pages).
      \item Back-End: Solid understanding of Python, R, and SQL (Data manipulation and analysis).
    \end{itemize}
  \item Data Science:
    \begin{itemize}
      \item Machine Learning (Intermediate - Exploring various algorithms and libraries)
    \end{itemize}
  \item Cloud Computing (Hands-on experience on PaaS)
  \item Internet of Things (Understanding of core concepts and protocols)
  \item Software Proficiency: MS Office Suite (Excel, Word, PowerPoint)
   \item CTF Competitions: Participated in CTF challenges on platforms like Hack The Box and TryHackMe, focusing on improving penetration testing and web security skills.
\end{itemize}



\section*{Hobbies}
Reading Books, Swimming, Photography

\section*{Declaration}
I declare that the information provided above is accurate and complete to the best of my knowledge.

\end{multicols}

\end{document}
